Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-11-03 chapters/chapter06.tex
swapping subsections, altering Outline

In this concluding chapter we start with highlighting some of the ongoing work, which revolves around using a promising family of priors driven by the Dirichlet process in order to model branch and site-specific parameters of codon substitution models.

Several aspects of the presented work are then put into a wider perspective, with possible extensions discussed in more detail.

Much of the work that constitutes this thesis resolves around relaxing the standard phylogenetic assumptions, in search of more biologically plausible models. 
In that light the work on the time-heterogenous modelling, as presented in Chapter \ref{chap:epoch}, can be viewed as an introductory step towards a broader range of models that tackle different types of time-heterogeneity.
We highlight one possible extension of the epoch model, in which time changes in a non-linear fashion.
We then discuss the possibility to infer both the time and the number of change-points, or transition times, in the epoch model specification via Dirichlet process priors discussed in the first section of this summarizing chapter.

>>>>

In this concluding chapter several aspects of the presented work are put into a wider perspective, with possible extensions discussed in more detail.

Much of the work that constitutes this thesis resolves around relaxing the standard phylogenetic assumptions, in search of more biologically plausible models. 
In that light the work on the time-heterogenous modelling, as presented in Chapter \ref{chap:epoch}, can be viewed as an introductory step towards a broader range of models that tackle different types of time-heterogeneity.
We highlight one possible extension of the epoch model, in which time changes in a non-linear fashion.
We then discuss the possibility to infer both the time and the number of change-points, or transition times, in the epoch model specification via Dirichlet process priors discussed in the second section of this summarizing chapter. 
We than highlight some of the ongoing work, which revolves around using a promising family of priors driven by the Dirichlet process in order to model branch and site-specific parameters of codon substitution models.
This work has been inspired by our utilization of substitution models in the full codon state space to infer the heterogenous patterns of diversifying selection in HIV infected patients.
